Interisland movements of woodland caribou in Newfoundland

### 2020-02-21 paper/manuscript.Rmd
Update manuscript.Rmd

# Individual variation 
In total, 3 of 29 collared female caribou swam between islands in the Fogo
archipelago. These swimming events were relatively frequent, on average occuring
once every 24 <!--double check--> days during ice-free seasons. However, despite
relatively frequent swimming events for these three individuals, we were unable
to identify any swimming events for the other 26 collared females. It remains
unclear why ocean swimming is relatively common among ~10% of our marked
population, while the other 90% never swam. Of the three collared individuals,
two were collared on Western Indian Island and the third was collared on Fogo
Island. It is possible that individuals born on, or that live on, Eastern and
Western Indian Island swim are more likely to swim between islands because
inter-island distances are shorter than between Western Indian and Fogo Islands
(Figure 2). Furthermore, it is unclear whether swimming is more common among
males or females. Our initial observation  was of an adult male, but our GPS
data only includes females. 
<!-- QW: I'm not sure we need to say this.. 
It is theoretically possible that these other
females moved rapidly back and forth between islands within the 2 hour fix rate
of our GPS collars, which we would be unable to detect. We consider this highly
unlikely given the range of residency times for caribou on any given island (min
- max: XX - XX). <!--double check-->
<!-- What is the typical residency time? Is this a true statement or am I just making this up? QW: this is something we will look into, I think. -->

@@

Our observations add to the evidence that caribou can, and occasionally do, swim
in the ocean (Table 1). While past observations (e.g.
@Jeffery_2007; @Ricca_2012] <!-- add Miller 1995, Miller 2002 --> have noted the
exceptional nature of caribou swimming in the ocean, we suggest that this
behaviour is likely more common than previously thought for caribou living on
oceanic islands. We posit forage limitation and the associated density-dependent
habitat selection is an ultimate explanation for why caribou swimming in the
ocean, with predator avoidance as a potential proximate explanation. Although
our inference is limited to observations, our observations suggest that islands
represent discrete foraging patches for terrestrial animals that could influence
fitness via increased foraging opportunities and safety from predators. We also
suggest that individuals vary in their evaluation of costs and benefits of
movement between these habitat patches.

>>>>

# Individual variation 
In total, 3 of 29 collared female caribou swam between islands in the Fogo
archipelago. These swimming events were relatively frequent, on average occuring
once every 24 <!--double check--> days during ice-free seasons. However, despite
relatively frequent swimming events for these three individuals, we were unable
to identify any swimming events for the other 26 collared females. It remains
unclear why ocean swimming is relatively common among ~10% of our marked
population, while the other 90% never swam. Of the three collared individuals,
two were collared on Western Indian Island and the third was collared on Fogo
Island. It is possible that individuals born on, or that live on, Eastern and
Western Indian Island swim are more likely to swim between islands because
inter-island distances are shorter than between Western Indian and Fogo Islands
(Figure 2). Furthermore, it is unclear whether swimming is more common among
males or females. Our initial observation  was of an adult male, but our GPS
data only includes females. <!-- QW: not sure how to finish this off -->
<!-- QW: I'm not sure we need to say this.. 
It is theoretically possible that these other
females moved rapidly back and forth between islands within the 2 hour fix rate
of our GPS collars, which we would be unable to detect. We consider this highly
unlikely given the range of residency times for caribou on any given island (min
- max: XX - XX). <!--double check-->
<!-- What is the typical residency time? Is this a true statement or am I just making this up? QW: this is something we will look into, I think. -->

@@

Our observations add to the evidence that caribou can, and occasionally do, swim
in the ocean (e.g. @Jeffery_2007; @Ricca_2012]. <!-- add Miller 1995, Miller
2002 -->  Taken together, we suggest that swimming is likely more common than
previously thought for caribou living on oceanic islands. We posit forage
limitation and the associated density-dependent habitat selection is an ultimate
explanation for why caribou swimming in the ocean, with predator avoidance as a
potential proximate explanation. Although our inference is limited to
observations, our observations suggest that islands represent discrete foraging
patches for terrestrial animals that could influence fitness via increased
foraging opportunities and safety from predators. We also suggest that
individuals vary in their evaluation of costs and benefits of movement between
these habitat patches.
